A generic and fast C++ optimization framework

### 2017-10-17 paper.tex
Update method/optimizer section.

% I guess to save some space we should group them.
\begin{itemize}
  \item {\bf SGD variants:} Vanilla SGD, SCD, SGDR, SMORMS3, AdaGrad, AdaDelta, RMSProp, Adam, AdaMax
  \item {\bf Quasi-Newton variants:} LBFGS, IQN, AugLagrangian
  \item {\bf Genetic variants:} CNE, CMA-ES
  \item {\bf Simulated Annealing}: Vanilla SA
  \item {\bf <TODO: add all things that we can optimize>}
\end{itemize}

>>>>

% I guess to save some space we should group them.
\begin{itemize}
  \item {\bf SGD variants:} Stochastic Gradient Descent (SGD), Stochastic
      Coordinate Descent (SCD), Parallel Stochastic Gradient Descent (Hogwild!),
      Stochastic Gradient Descent with Restarts (SGDR), SMORMS3, AdaGrad,
      AdaDelta, RMSProp, Adam, AdaMax

  \item {\bf Quasi-Newton variants:} Limited-memory BFGS (L-BFGS), incremental
        Quasi-Newton method (IQN), Augmented Lagrangian Method

  \item {\bf Genetic variants:} Conventional Neuro-evolution (CNE), Covariance
        Matrix Adaptation Evolution Strategy (CMA-ES)

  \item Simulated Annealing

  \item Frank-Wolfe algorithm

  \item {\bf Objective functions:} Neural Networks, Logistic regression,
      Matrix completion, Neighborhood Components Analysis, Regularized SVD,
      Reinforcement learning, Softmax regression, Sparse autoencoders,
      Sparse SVM
\end{itemize}

In addition, many methods are currently in development and will be released in
the future.
